You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-25 paper/paper.tex
added figures

\subsubsection{Dictionary Based Paraphrase}
Several dictionaries of stylistically representative words of Shakesperean English and their modern equivelants are available on the web.  These dictionaries can be used 
to define a translation model which is used in combination with a language model as in standard phrase-based MT \cite{knight}.

@@

\subsubsection{Out of Domain Monolingual Parallel Data}
As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of doimain parallel text, with an in-domain
language model consisting of Shakespeare's 37 plays.

\subsection{Comparison Using Automatic Evaluation Metrics}
\begin{itemize}
  \item List the various systems we evaluate (e.g. varying LM size, etc...)
  \item Plot BLEU and PINC scores for the various systems
\end{itemize}

>>>>

\subsubsection{Dictionary Based Paraphrase}
Several dictionaries of stylistically representative words of Shakesperean English and their modern equivelants are available on the web.  These dictionaries can be used 
to define a translation model which is used in combination with a language model as in standard phrase-based MT \cite{Koehn00}.

@@

\subsubsection{Out of Domain Monolingual Parallel Data}
As a final baseline we consider a paraphrase system which is trained on out-of-domain data gathered by asking users of Amazon's Mechanical Turk Service 
\cite{Snow08} to describe videos \cite{chen11}.  We combine a phrase table extracted from this out of doimain parallel text, with an in-domain
language model consisting of Shakespeare's 37 plays.  Although this monolingual parallel data does not include text in the target writing style,
the in-domain language model does bias the generated sentences towards Shakespeare's writing style.

\subsection{Comparison Using Automatic Evaluation Metrics}
Figure \ref{bleupinc} compares a variety of sytstems targeting Shakesperean English using previously the previosly proposed BLEU \cite{Papineni02} and PINC \cite{chen11} automatic evaluation metrics.

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[width=2.1in]{figures/bleupinc1.pdf} & \includegraphics[width=2.1in]{figures/bleupinc2.pdf} \\
    \end{tabular}
  \end{center}
  \caption{Various Shakesperean Paraphrase systems compared using BLEU and PINC.}
  \label{bleupinc}
\end{figure}

\begin{itemize}
  \item List the various systems we evaluate (e.g. varying LM size, etc...)
  \item Plot BLEU and PINC scores for the various systems
\end{itemize}
